---
output: html_notebook
---

Załaduj tidyverse
```{r}
library(tidyverse)
library(tidyselect)
```

Stwórz df z csv z danymi z openpsychometrics.org
```{r}
RSE <- read_tsv("~/Robota/ZAJECIA_psychometria/RSE-data/data.csv")
problems(RSE)
print(RSE)
```

Dane do czyszczenia
```{r}
count(RSE)

q_cols <- colnames(RSE)[1:10]
RSE <- RSE %>% 
  mutate_at(q_cols, na_if, y=0) %>% 
  mutate_at(q_cols, as_factor)

for (.q in seq_along(q_cols)) {
  print(q_cols[.q])
  print(table(RSE[.q], useNA = "always"))
}

#wywal wszystkie linijki, w których jest missing
RSE <- RSE %>% 
  drop_na(Q1:Q10)

for (.q in seq_along(q_cols)) {
  print(q_cols[.q])
  print(table(RSE[,.q], useNA = "always"))
}

count(RSE)
```

Policz punkty:
1=strongly disagree, 
2=disagree, 
3=agree,  
4=strongly agree
Items 3, 5, 8, 9, and 10 reversed in valence
Q1. I feel that I am a person of worth, at least on an equal plane with others.	
Q2. I feel that I have a number of good qualities.	
Q3. All in all, I am inclined to feel that I am a failure.	
Q4. I am able to do things as well as most other people.	
Q5. I feel I do not have much to be proud of.	
Q6. I take a positive attitude toward myself.	
Q7. On the whole, I am satisfied with myself.	
Q8. I wish I could have more respect for myself.	
Q9. I certainly feel useless at times.	
Q10. At times I think I am no good at all.
```{r}
#Itemy wprost (1,2,4,6,7)
RSE <- RSE %>%
  mutate(P1 = case_when(
    Q1 == 1 ~ 0, 
    Q1 == 2 ~ 1,
    Q1 == 3 ~ 2,
    Q1 == 4 ~ 3))

RSE <- RSE %>%
  mutate(P2 = case_when(
    Q2 == 1 ~ 0, 
    Q2 == 2 ~ 1,
    Q2 == 3 ~ 2,
    Q2 == 4 ~ 3))

RSE <- RSE %>%
  mutate(P4 = case_when(
    Q4 == 1 ~ 0, 
    Q4 == 2 ~ 1,
    Q4 == 3 ~ 2,
    Q4 == 4 ~ 3))

RSE <- RSE %>%
  mutate(P6 = case_when(
    Q6 == 1 ~ 0, 
    Q6 == 2 ~ 1,
    Q6 == 3 ~ 2,
    Q6 == 4 ~ 3))

RSE <- RSE %>%
  mutate(P7 = case_when(
    Q7 == 1 ~ 0, 
    Q7 == 2 ~ 1,
    Q7 == 3 ~ 2,
    Q7 == 4 ~ 3))

#Itemy odwrócone (3,5,8,9,10)
RSE <- RSE %>%
  mutate(P3 = case_when(
    Q3 == 1 ~ 3, 
    Q3 == 2 ~ 2,
    Q3 == 3 ~ 1,
    Q3 == 4 ~ 0))

RSE <- RSE %>%
  mutate(P5 = case_when(
    Q5 == 1 ~ 3, 
    Q5 == 2 ~ 2,
    Q5 == 3 ~ 1,
    Q5 == 4 ~ 0))

RSE <- RSE %>%
  mutate(P8 = case_when(
    Q8 == 1 ~ 3, 
    Q8 == 2 ~ 2,
    Q8 == 3 ~ 1,
    Q8 == 4 ~ 0))

RSE <- RSE %>%
  mutate(P9 = case_when(
    Q9 == 1 ~ 3, 
    Q9 == 2 ~ 2,
    Q9 == 3 ~ 1,
    Q9 == 4 ~ 0))

RSE <- RSE %>%
  mutate(P10 = case_when(
    Q10 == 1 ~ 3, 
    Q10 == 2 ~ 2,
    Q10 == 3 ~ 1,
    Q10 == 4 ~ 0))

RSE <- RSE %>% mutate(TOTAL = P1+P2+P3+P4+P5+P6+P7+P8+P9+P10)
 
```

Zapisz nową csv z samymi punktami
```{r}
RSE_P <- select(RSE, starts_with("P"), TOTAL, gender, age, source, country)
write_tsv(RSE_P, "data_scores.csv")
```

