# Setup

Żeby zadziałał import, musisz zapisać plik dane_clean.csv i ten notatnik w jendym folderze!

Importowane wyniki pochodzą stąd: https://openpsychometrics.org (access 14 Nov 2019) a tu możecie poczytać o opracowanej skali: https://openpsychometrics.org/tests/NPAS/development/

Będziecie pracować na fragmencie tego zbioru.

```{r}
NPAS <- read.delim("data_clean.csv")
NPAS <- NPAS[501-1000, ]
NPAS_items <- c("Q1", "Q2", "Q3", "Q4", "Q5", "Q6", "Q7", "Q8", "Q9", "Q10", "Q11", "Q12", "Q13", "Q14", "Q15", "Q16", "Q17", "Q18", "Q19", "Q20", "Q21", "Q22", "Q23", "Q24", "Q25", "Q26")
NPAS$total <- apply(NPAS[ , NPAS_items], 1, sum)

my_reverse <- function(item, min, max) {
  max - (item - min)
}

NPAS$ekstrawersja <- NPAS$TIPI1 + my_reverse(NPAS$TIPI6, 1, 7)
NPAS$ugodowosc <- my_reverse(NPAS$TIPI2, 1, 7) + NPAS$TIPI7

NPAS <- NPAS[ , c(NPAS_items, "total", "ekstrawersja", "ugodowosc")]
```

Poszczególne pytania NPAS:

Q1  I am interested in science.
Q2  I was in advanced classes.
Q3  I like to play RPGs. (Ex. D&D)
Q4  My appearance is not as important as my intelligence.
Q5  I collect books.
Q6  I prefer academic success to social success.
Q7  I watch science related shows.
Q8  I spend recreational time researching topics others might find dry or overly rigorous.
Q9  I like science fiction.
Q10 I would rather read a book than go to a party.
Q11 I am more comfortable with my hobbies than I am with other people.    
Q12 I spend more time at the library than any other public place.
Q13 I would describe my smarts as bookish.
Q14 I like to read technology news reports.
Q15 I have started writing a novel.
Q16 I gravitate towards introspection.
Q17 I am more comfortable interacting online than in person.
Q18 I love to read challenging material.
Q19 I have played a lot of video games.
Q20 I was a very odd child.
Q21 I sometimes prefer fictional people to real ones.
Q22 I enjoy learning more than I need to.
Q23 I get excited about my ideas and research.
Q24 I am a strange person.
Q25 I care about super heroes.
Q26 I can be socially awkward at times.

# Podejrzyj dane

```{r}
head(...)
```

# Jakie macie hipotezy dotyczące związku bycia nerdem z...

1. ekstrawersją
2. ugodowością

# Zbadajcie korelację bycia nerdem z tymi zmiennymi

Policz korelację wyniku ogólnego z ekstrawersją i ugodowością.

```{r}
cor(..., ...)
cor(..., ...)
```

# Czy był to zbieżny czy rozbieżny aspekt trafności?
